An Analysis of Preference and Percieved Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender: Men and Women Both Prefer and Percieve Inaction as More Competent

### 2024-02-15 outputs/paper/paper.qmd
paper update

---
title: "Is There a Correlation Between Preference and Perceptions of Inaction and Action in Decision-Making and Gender? An Analysis of Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes Study 2."
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This paper investigates the correlation between preference and perceptions of inaction versus action in decision-making and gender to replicate on the previous studies about the findings regarding gender disparities in moral judgment preference. Building on interdisciplinary research in cognitive science, psychology, and philosophy, the study explores and examines the preference and perceived competence of different decision-making agents by gender. This report uses the  Study 2 data set from the article “Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes” for creating graphs and conducting statistical analysis. Since this research topic can be significant for further research, we place more weight on the discussion and further research section to inform and address the interplay of social factors."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---

```{r}
#| message: false
#| echo: false
#| warning: false
#### Workspace set-up ####

## Load packages
library(tidyverse)
library(ggplot2)
library(knitr)

@@

histogram_male <- ggplot(data_male, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  scale_y_continuous(limits = c(0,140), breaks = seq(0, 140, by = 10)) +
  labs(title = "Distribution of Males by Preference",
       x = "Preference",
       y = "Frequency") +
  theme_minimal()
histogram_male
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencefemale
#| fig-cap: Frequency of Decision-Making Approach Preference Responses Across Women

histogram_female <- ggplot(data_female, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  scale_y_continuous(limits = c(0,140), breaks = seq(0, 140, by = 10)) +
  labs(title = "Distribution of Females by Preference",
       x = "Preference",
       y = "Frequency") +
  theme_minimal()
histogram_female
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferenceboth
#| fig-cap: Comparison of Decision-Making Approach Preference Response Frequencies by Gender

# Preference Comparison Graph 
histogram_comparison_preference <- ggplot(data_gender, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Comparison of Preference Distribution by Gender",
       x = "Preference",
       y = "Frequency") +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  facet_wrap(~gender, scales = "free")
histogram_comparison_preference
```

@@

# Competence Graph by Gender 1 (Male)
histogram_male_competence <- ggplot(data_male, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Males by Competence ",
       x = "Competence",
       y = "Frequency") +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  theme_minimal()
histogram_male_competence
```

@@

# Competence Graph by Gender 2 (Female)
histogram_female_competence <- ggplot(data_female, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Females by Competence",
       x = "Competence",
       y = "Frequency") +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  theme_minimal()
histogram_female_competence
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competenceboth
#| fig-cap: Comparison of Percieved Competence Participant Response Frequencies by Gender

# Competence Comparison Graph 
histogram_comparison_competence <- ggplot(data_gender, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Comparison of Competence Distribution by Gender",
       x = "Preference",
       y = "Frequency") +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  facet_wrap(~gender, scales = "free")
histogram_comparison_competence
```

>>>>

---
title: "An Analysis of Preference and Percieved Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender: Men and Women Both Prefer and Percieve Inaction as More Competent"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This paper investigates the correlation between preference and perceptions of inaction versus action in decision-making and gender to replicate on the previous studies about the findings regarding gender disparities in moral judgment preference. Building on interdisciplinary research in cognitive science, psychology, and philosophy, the study explores and examines the preference and perceived competence of different decision-making agents by gender. This report uses the  Study 2 data set from the article “Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes” for creating graphs and conducting statistical analysis. Since this research topic can be significant for further research, we place more weight on the discussion and further research section to inform and address the interplay of social factors."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---

```{r}
#| message: false
#| echo: false
#| warning: false
#### Work space set-up ####

## Load packages
library(tinytex)
library(tidyverse)
library(ggplot2)
library(knitr)

@@

histogram_male <- ggplot(data_male, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  scale_y_continuous(limits = c(0,140), breaks = seq(0, 140, by = 10)) +
  labs(title = "Frequency of Preference Responses (Men)",
       x = "Preference",
       y = "Frequency") +
  theme_minimal()
histogram_male
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencefemale
#| fig-cap: Frequency of Decision-Making Approach Preference Responses (Women)

histogram_female <- ggplot(data_female, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  scale_y_continuous(limits = c(0,140), breaks = seq(0, 140, by = 10)) +
  labs(title = "Frequency of Preference Responses (Women)",
       x = "Preference",
       y = "Frequency") +
  theme_minimal()
histogram_female
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferenceboth
#| fig-cap: Comparison of Decision-Making Approach Preference Response Frequencies by Gender, Men = 1 and Women = 2

# Preference Comparison Graph 
histogram_comparison_preference <- ggplot(data_gender, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Comparison of Preference Response Frequencies by Gender",
       x = "Preference",
       y = "Frequency") +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  facet_wrap(~gender, scales = "free")
histogram_comparison_preference
```

@@

# Competence Graph by Gender 1 (Male)
histogram_male_competence <- ggplot(data_male, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Frequency of Competence Responses (Men)",
       x = "Competence",
       y = "Frequency") +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  theme_minimal()
histogram_male_competence
```

@@

# Competence Graph by Gender 2 (Female)
histogram_female_competence <- ggplot(data_female, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Frequency of Competence Responses (Women)",
       x = "Competence",
       y = "Frequency") +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  theme_minimal()
histogram_female_competence
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competenceboth
#| fig-cap: Comparison of Percieved Competence Participant Response Frequencies by Gender, Men = 1 and Women = 2

# Competence Comparison Graph 
histogram_comparison_competence <- ggplot(data_gender, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Comparison of Competence Response Frequencies by Gender",
       x = "Preference",
       y = "Frequency") +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  facet_wrap(~gender, scales = "free")
histogram_comparison_competence
```
